Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-06-05 paper/paper.tex
Fix bibliography error

% bibliography
\usepackage[english]{babel}
\usepackage[backend=biber, bibencoding=utf8, style=authoryear, citestyle=authoryear-comp, date=year, maxbibnames=6, minbibnames=6, url=false, isbn=false, autocite=inline]{biblatex}
\addbibresource{Bibliography.bib}

>>>>

% bibliography
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage[
backend=biber, 
bibencoding=utf8, 
style=authoryear, 
date=year, 
maxbibnames=6, 
minbibnames=6, 
url=false, 
isbn=false, 
eprint=false,
uniquename = false, 
autocite=inline]{biblatex}
\addbibresource{Bibliography.bib}
